% Created 2021-09-10 Fri 21:10
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{tikz}
\author{manuel.fuica.morales@gmail.com}
\date{10 September 2021}
\title{Generation of Tikz pictures using SVG for Org Mode html export option.\\\medskip
\large suited for a Doom Emacs distribution.}
\hypersetup{
 pdfauthor={manuel.fuica.morales@gmail.com},
 pdftitle={Generation of Tikz pictures using SVG for Org Mode html export option.},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.5)}, 
 pdflang={English}}
\begin{document}

\maketitle
\setcounter{tocdepth}{2}
\tableofcontents


\section{About SVG file format}
\label{sec:org55c7a3c}

\subsection{What is it?}
\label{sec:org0e851df}
\subsection{How does it relate to  \LaTeX}
\label{sec:org4b42a9c}
This is some text.
\subsection{How does it relate to html ?}
\label{sec:orgf3588a3}



\section{Backend dependent execution -- conditionally export tikz to SVG on HTML export}
\label{sec:orgd3e58e2}

This example demonstrates the handling of a \LaTeX{} code block
differently depending on the export backend.  If the following file is
exported to HTML the tikz code block will be converted to an SVG
images, while on export to pdf (through \LaTeX{}) the tikz code will
simply be inserted into the document verbatim.

First execute the second code block, to define the convenience macro
and to set the required new variables in ob-latex.el.  Then export to
HTML and to pdf to see the tree exported as an SVG image and as
embedded tikz respectively.

\section{Tikz test}
\label{sec:org83b738b}
Here's a tree, exported to both html and pdf.


This allows for the automatic composition of beautiful scalable
graphics across both HTML and pdf from a single document and image
source.
\end{document}
